Coupling microsimulation models with land-use transport models

### 2019-01-18 main.tex
matsim
Update on Overleaf.

\input{header.tex}

@@

%\author{\noun{Juste Raimbault}}
\date{}

@@

The QUANT land-use transport interaction model \cite{batty2019generalized} responds to this constraints as it integrates fine data for population, employments and transportation at the scale of all UK, while keeping a simple and interpretable structure in the process implemented. Integrating it with a complementary model, possibly at an other scale, would open new possibilities for the design of territorial policies.

@@

The literature is rather sparse on studies coupling spatial interaction models with microsimulation models. Examples include configurations where the spatial and demographic structure of population plays a role in its interaction with the object of study, such as retail \cite{Nakaya2007}, or in spatial epidemiology. Beside possible policy applications, our approach can therefore also provide methodological contributions.

@@

% \section{Other directions}
% microsim models with other ontologies, e.g. Matsim for transportation ?

>>>>

\input{header.tex}
\begin{document}

@@

%\author{}
\date{}

@@

The QUANT land-use transport interaction model \cite{batty2019generalized} responds to this constraints as it integrates fine data for population, employments and transportation at the scale of all UK, while keeping a simple structure for the processes implemented. Integrating it with a complementary model, possibly at an other scale, would open new possibilities for the design of territorial policies.

@@

The literature is rather sparse on studies coupling spatial interaction models with microsimulation models. Examples include configurations where the spatial and demographic structure of population plays a role in its interaction with the object of study, such as retail \cite{Nakaya2007}, in spatial epidemiology \cite{morrissey2010examining}, or for socio-spatial simulations of a particular population \cite{wu2008spatial}. Beside possible policy applications, our approach can therefore also provide methodological contributions.

@@

\section{Other perspectives}

% microsim models with other ontologies, e.g. Matsim for transportation ?

\begin{itemize}
	\item Matsim is an agent-based approach to transportation demand which is activity-based \cite{horni2016multi}. It can simulate agents behavior within the transportation system (traffic flows) and behavioral patterns generating the travel demand. According to \cite{wise2016transportation}, accurate description of transportation remains a point to be explored for agent-based model. A weak coupling of Quant and Matsim would be interesting in that sense, and allow to precisely explore the consequence of transportation scenarios.
	\item More generally, the fuzzy boundary between microsimulation and agent-based modeling may be an interesting point to be investigated, both methodologically and theoretically.
\end{itemize}
